\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{enumerate}[label={[{\arabic*}]},leftmargin=1.2cm,labelsep=0.3cm]

  
    %\item J. Gubbi, R. Buyya, S. Marusic và M. Palaniswami, ``Internet of
    %Things (IoT): A vision, architectural elements, and future directions,''
    %\textit{Future Generation Computer Systems}, doi: 10.1016/j.future.2013.01.010.

    \item NestJS, ``NestJS Documentation.'' [Trực tuyến]. Địa chỉ:
    \url{https://docs.nestjs.com/}. Truy cập ngày 23/06/2026.

    \item PostgreSQL Global Development Group, ``PostgreSQL
    Documentation.'' [Trực tuyến]. Địa chỉ:
    \url{https://www.postgresql.org/docs/current/}. Truy cập ngày
    23/06/2026.

    \item Google, ``Flutter Documentation.'' [Trực tuyến]. Địa chỉ:
    \url{https://docs.flutter.dev/}. Truy cập ngày 23/06/2026.

    \item Google, ``Dart Overview.'' [Trực tuyến]. Địa chỉ:
    \url{https://dart.dev/overview}. Truy cập ngày 23/06/2026.

    \item Espressif Systems, ``ESP32 Series Datasheet.'' [Trực tuyến].
    Địa chỉ:
    \url{https://www.espressif.com/sites/default/files/documentation/esp32_datasheet_en.pdf}.
    Truy cập ngày 23/06/2026.

    \item OASIS Open, ``MQTT Version 3.1.1 Plus Errata 01,'' 2015.
    [Trực tuyến]. Địa chỉ:
    \url{https://docs.oasis-open.org/mqtt/mqtt/v3.1.1/os/mqtt-v3.1.1-os.html}.
    Truy cập ngày 23/06/2026.

    \item Prisma Data, Inc., ``Prisma ORM Documentation.'' [Trực tuyến].
    Địa chỉ: \url{https://www.prisma.io/docs/orm}. Truy cập ngày
    23/06/2026.

    \item OpenStreetMap Foundation, ``About OpenStreetMap.'' [Trực tuyến].
    Địa chỉ: \url{https://www.openstreetmap.org/about}. Truy cập ngày
    23/06/2026.

    \item R. W. Sinnott, ``Virtues of the Haversine,'' \textit{Sky and
    Telescope}, tập 68, số 2, tr. 159, 1984.

    \item Socket.IO, ``Socket.IO Documentation, Version 4.'' [Trực tuyến].
    Địa chỉ: \url{https://socket.io/docs/v4/}. Truy cập ngày 23/06/2026.

    \item Google, ``Firebase Cloud Messaging Documentation.''
    [Trực tuyến]. Địa chỉ:
    \url{https://firebase.google.com/docs/cloud-messaging}. Truy cập ngày
    23/06/2026.

    \item M. B. Jones, J. Bradley và N. Sakimura, ``JSON Web Token
    (JWT),'' Internet Engineering Task Force, RFC 7519, 2015,
    doi: 10.17487/RFC7519. [Trực tuyến]. Địa chỉ:
    \url{https://www.rfc-editor.org/rfc/rfc7519}.


\end{enumerate}

\end{document}
